% !TEX root = ../../seminar.tex

\newpage
\subsection{Checklist}

(make notes/documentation of the following points)


Formulate Question
	Description
		Contains technology in a context showing an effect.
	
	Guidelines
		Create question using a structued apporoach such as PICOT. 
		Validate question with FINER.
	
	Checklist
		\# Question systematically constructed
		\# Question's formulation validated			
				
				
Formulate Hypothesis
	Description
		A testable prediction based on the question.

	Guidelines
		Contains: 2 or more variables, context, relationship between the variables
		?If [I do this], then [this] will happen.? TODO vs. ?If I [do X], then [Y] will happen.?
		
	Checklist
		\# Hypothesis is formulated as prediction
		\# Prediction is testable
		
Search For Existing Evidence
	Description
		Search for evidence related to the research question.
		Deepen your understanding of the reasearch domain.
		If necessary, incrementally refine the research question.
	
	Guidelines
		Use 'Cited by' function of search engines
		Read through found work's bibliography
		Refer to Systematic Literature Reviews for a wide comparison of related work
		Find similar work using classification systems such as CCS [http://dl.acm.org/ccs/ccs.cfm]
		If looking for alternatives, use search engine's autocomplete "x vs ..."
		Note search strings for more structured search approach
		Too few search results? Make Reseach Question more general.
		Too many/general search results? Narrow down Reseach Question.
		
	Checklist
		\# Rough understanding/overview
		\# Deep understanding
		\# Critical appraisal of relevant related work
	
	
Experiment	
	Description
		Design, Conduct and Evaluate Experiment.
		TODO !recursive!
	
	Guideline
		TODO reference to [Experimenting in Software Engineering]
		Use Briefing Form
		
	Checklist
		\# Experiment Designed
		\# Experiment Conducted
		\# Experiment Evaluated
		\# Briefing Form filled in
		

Answer Question
	Description
		Accept or reject Hypothesis based on evidence.
		Answer the Research Question accordingly.
	
	Guideline
		Make sure evidence is substantial enough to answer the Reseach Question.
		Try to avoid bias. (Confirmation Bias, Information Expectancy Bias, ...)
		
	Checklist
		\# Hypothesis' validity is evaluated
		\# Research Question is answered
	
	
Discussion
	Description
		Discuss the whole study, suggest future approaches and limits.
		
	Guideline
		Critically assess study using EBSE checklist \cite[p. 62]{Dyba2005}.
		Put study in relation to larger context.

	Checklist
		\# Content of study critically assesed
		\# Study put in larger context



Eval Process
	Description
		Reflect on your work in the previous steps and seek ways to improve your
		future performance.
		
	Guideline	
		Use After Action Review and Postmortem Analysis \cite{Dyba2005}.
		TODO insert AAR, PMA
		
	Checklist	
		\# AAR done
		\# PMA done
		\# Conclusions drawn for future processes
	
	
	
	
	