\subsection{Structured Abstract}

\todo{importance of abstracts}: Abstracts, together with the title, are used to identify relevant research, not only in SLRs. Often the abstract is the only part of the paper that can be accessed for free. Therefore abstract and title should contain all necessary information to decide whether a paper (in case of SLR: primary study) is relevant in this context. (source: \q{Lessons from applying the systematic literature review process within the software engineering domain})
	$\rightarrow$ quality of abstract crucial for research, how to support researcher in writing useful abstracts? Structured Abstracts provide guidance for writer and reader. \red{end TODO}
\newline

In their guidelines for reporting experiments in software engineering Jedlitschka et al. \cite{Jedlitschka2008} propose the use of \emph{structured abstracts}. They adopted the idea from medicine and psychology, where structured abstracts were introduced to increase the quality of abstracts. Although a variety of different elements is used (see for example \q{Adoption of structured abstracts by general medical journals and format for a structured abstract
}), the most common elements of structured abstracts are \emph{Background} (\emph{or Context}), \emph{Objective} (or \emph{Aim}), \emph{Methods}, \emph{Results} and \emph{Conclusion} (or \emph{Discussion}). Jedlitschka et al. \cite{Jedlitschka2008} suggest the use of a 6th (\todo{or sixth?} heading called \emph{limitations}. This information is necessary to decide whether a result can be transfered to another context. Others \todo{often? mostly?} (e.g. Kitchenham et al. \cite{KBO2008}) include this information in the \emph{conclusion} section.

The list and description of elements below closely follows the suggestion of Jedlitschka et al.\cite{Jedlitschka2008}.
\begin{enumerate}
	\item \textbf{Background} or \textbf{Context}: Explain briefly what the motivation for conducting the study was and refers to previous research.
	\item \textbf{Objective} or \textbf{Aim}: Describes the purpose of the study, including the object that is studied as well as focus and perspective. \todo{research question or hypotheses?}
	\item \textbf{Methods}: Sums up which research methods were used, for example experimental design, setting, participants and selection criteria, intervention and measurement and analyzing technique.
	\item \textbf{Results}: The key findings are described here in form of numerical values. \todo{name stat. significance, confidece interval, standard error?} (Do not include interpretations here!).
	\item \textbf{Limitations}: Describes the scope  of the study to point out the limits of generalization (This element might be incorporated in the \emph{conclusion}-element).
	\item \textbf{Conclusion}:  Contains the interpretation of results and puts them into context.
\end{enumerate}
\todo{examples? keywords as part of abstract?}

There are several studies comparing structured and unstructured abstracts in the domain of software engineering with regard to completeness and clarity \todo{noting the similar authors (weakening the statement)?}:

\begin{itemize}
\item Structured abstracts include more relevant information and are easier to read than conventional abstracts \cite{Budgen2007,Budgen2008}.
\item Inexperienced authors are likely to produce clearer and more complete abstracts when using a structured form \cite{Budgen2011} .
\item On average structured abstracts are longer (limitations in conclusion is a good idea to prevent lengthy abstracts) and have better readability than unstructured abstracts \cite{KBO2008}.
\end{itemize}
	
These findings are consistent with the ones in other disciplines. It is important to mention that there are critics of structured abstracts that are supported by studies, but in general structured abstracts are considered advantageous \cite{hartley2004,hartley2014}.	

A downside to structured abstracts is their length (compared to unstructured ones). If the size of abstracts is limited, the abstract should still be in a structured form traditional elements should be prioritized: background (one sentence), objective, methods, result and conclusion \cite{Jedlitschka2008}.

If it is not possible to structure an abstract (e.g. due to standard of journal or supervisor, length limitations) the elements of a structured abstracts should be contained in the unstructured abstract to make sure no important information is missing (see the common structure of the clearest abstracts found by Shaw \cite{shaw2003}). Moreover the reader should be able to quickly identify the elements by reading through the abstract.
\newline
\newline
\todo{notes and ideas}
\begin{itemize}	
\item Elements similar to \q{IMRAD}-structure (see paper \q{Adoption of structured abstracts by general medical journals and format for a structured abstract})	
\item guidelines for construcing structured abstracts (from unstructered ones) in \cite{KBO2008} $\rightarrow$ used to verify descr of elements
\item Guide with examples (psychology): \q{How to write a good abstract for scientific paper.}, C. Andrade
	\newline
	ANSI/NISO Z39.14.1997 (R2015) Guidelines for Abstracts
\item use standard terminology (commonly used industry terms) \cite{Jedlitschka2008}, no abbreviations \cite{KBO2008}
\end{itemize}
\red{end TODO}